---
title: "Hospital"
author: "Amanda Molling"
date: "Monday, March 23, 2015"
output: html_document
---
# Plot the 30-day mortality rates for heart attack

```{r}
outcome <-read.csv("outcome-of-care-measures.csv", colClasses = "character")
head(outcome)

outcome[,11] <- as.numeric(outcome[,11])
hist(outcome[,11])
```

```{r}
best <- function(state = "", outcome = ""){
    ## Function that reads the outcome of care csv and return the name of the hospital with the best results for 30 days for that cause of death.
 
  ## Read outcome data
 ## data <- read.csv(unzip("https://d396qusza40orc.cloudfront.net/rprog%2Fdata%2FProgAssignment3-data.zip"), colClasses = "character")
  
  
  data <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
  
  
  ## check that state and outcome are valid
  state <- toupper(state)
  outcomes <- c("heart attack", "heart failure", "pneumonia")
  
  testState <- ( is.element ( state, state.abb ) )  
  
  testOutcome <- ( is.element ( outcome, outcomes ))
                                                      
 if (!testState){
   stop("invalid state")
 } 
 if (!testOutcome){
   stop("invalid outcome")
 }
  else if (  (testState) & (testOutcome) ){
        print("test passed")
        if (outcome == "heart attack")
          search <- "Hospital.30.Day.Death..Mortality..Rates.from.Heart.Attack"
          print(data[1,"Hospital.30.Day.Death..Mortality..Rates.from.Heart.Attack"])    
    }
  
 

  ## Return hospital name in that state w/lowest 30-day death. 
}

